\LARGE \bf Energy-Aware Dynamic Mission Planning Algorithm for UAVs

### 2020-11-27 icra-2021.tex
hopefully this is the last change to intro for long time...

Many scenarios involving unmanned aerial vehicles (UAVs), such as precision agriculture, search and rescue, and surveillance, require high autonomy but have limited energy budgets. A typical example of a mission in these scenarios is a UAV flying a path--that can be composed of multiple trajectories--and performing some on-board computational tasks. For instance, the UAV might detect ground patterns and inform other ground-based actors with little human interaction. We refer to the computational tasks that can be dynamically replanned as computations. We are interested in energy-aware dynamic mission planning, which would find optimal tradeoffs between the path, computations, and energy requirements. Current generic planning solutions for outdoor UAVs do not plan the mission dynamically, nor are energy-aware. They are often semi-autonomous; the mission is static and usually defined using mission planning software~\cite{daponte2019review}. Such a state of practice has prompted us to propose an \emph{energy-aware dynamic mission planning algorithm} for UAVs. The algorithm combines and generalizes some of the past body of knowledge on mobile robot planning problems and addresses the increasing \emph{computational demands} and their relation to energy consumption, path, and autonomy for the UAV mission planning problem.

@@

Unlike most of the past planning algorithms literature, our algorithm plans both the computations and path. We guide the UAV using a vector field~\cite{de2017guidance} that converges smoothly to a planned trajectory. The use of vector fields for planning is widely discussed in the literature~\cite{lindemann2005smoothly,gonccalves2010vector,panagou2014motion,zhou2014vector,kapitanyuk2017guiding}. To express a trajectory, we use a mathematical function that we refer to as the trajectory explicit equation (TEE). We plan the computations using a modeling tool presented in our previous work~\cite{seewald2019coarse}. In our approach, the user specifies an initial mission plan--the path using the TEEs, computations, energy budget, and some parameters. The parameters are the maximum, minimum, and current levels of the computations and trajectory. The energy budget is the battery capacity and some other battery parameters. The algorithm replans the initial mission plan as the remaining battery state of charge (SoC) unexpectedly changes due to, e.g., atmospheric interferences. Our goal is to complete the mission with the highest possible current computations and trajectory parameters as the UAV flies and its batteries drain. In the remainder of the paper, we adopt the following notation. We refer to the current computations and trajectory parameters simply as computations and trajectory parameters. We refer to both as parameters. We refer to the constraints sets that delimit the maximum and minimum level of parameters as computations sets and trajectory sets. There can be multiple or none computations sets per each task, and the same applies to the trajectory. The term parameters should not be confused with the battery parameters, which we always mention explicitly. These are fixed values that are not replanned by the algorithm. The algorithm outputs the parameters using output model predictive control (MPC).

>>>>

Many scenarios involving unmanned aerial vehicles (UAVs), such as precision agriculture, search and rescue, and surveillance, require high autonomy but have limited energy budgets. A typical example of a mission in these scenarios is a UAV flying a path and performing some on-board computational tasks. For instance, the UAV might detect ground patterns and inform other ground-based actors with little human interaction. We refer to the computational tasks that can be dynamically replanned as computations. We are interested in energy-aware dynamic mission planning, which would find optimal tradeoffs between the path, computations, and energy requirements. Current generic planning solutions for outdoor UAVs do not plan the mission dynamically, nor are energy-aware. They are often semi-autonomous; the mission is static and usually defined using mission planning software~\cite{daponte2019review}. Such a state of practice has prompted us to propose an \emph{energy-aware dynamic mission planning algorithm} for UAVs. The algorithm combines and generalizes some of the past body of knowledge on mobile robot planning problems and addresses the increasing \emph{computational demands} and their relation to energy consumption, path, and autonomy for the UAV mission planning problem.

@@

Unlike most of the past planning algorithms literature, our algorithm plans both the path and computations. We guide the UAV using a vector field~\cite{de2017guidance} that converges smoothly to a planned trajectory. The use of vector fields for planning is widely discussed in the literature~\cite{lindemann2005smoothly,gonccalves2010vector,panagou2014motion,zhou2014vector,kapitanyuk2017guiding}. We denote the trajectory with a mathematical function that we refer to as the trajectory explicit equation (TEE). The path is composed of multiple TEEs. We express the computations with a modeling tool presented in our previous work~\cite{seewald2019coarse}. The algorithm alters the TEE and computations within some parameters using output model predictive control (MPC). These parameters are the maximum, minimum, and current levels of the TEE and computations. The user specifies the parameters in an initial mission plan with an energy budget. The energy budget is the battery capacity and some other battery parameters. In the remainder of the paper, we adopt the following notation. We refer to the current TEE and computations parameters simply as TEE and computations parameters. We refer to both as parameters. We refer to the constraints sets that delimit the maximum and minimum levels of the parameters as TEE sets and computations sets. There can be multiple or none computations sets per each task, and the same applies to the TEE. The term parameters should not be confused with the battery parameters, which we always mention explicitly. These are fixed values that are not replanned by the algorithm. Our goal is to complete the mission with the highest possible parameters as the UAV flies and its batteries drain.
